---
title: "Reproducible Research: Peer Assessment 1"
output: 
  html_document:
    keep_md: true
---


## Loading and preprocessing the data
We use the ```ggplot2``` package to plot the data:
```{r}
library(ggplot2)
```

The data is a available in a ZIP file, we can extract the data and read it in to a data frame:
```{r}
unzip("activity.zip")
activity <- read.csv("activity.csv")
```

TODO: preprocess

## What is mean total number of steps taken per day?

From the activity data, we create an array of the number of steps taken per day:
```{r }
stepsPerDay <- tapply(activity$steps, activity$date, sum, na.rm = TRUE)
```

We display this this data in a histogram showing the distribution of steps per day.
```{r }
qplot(stepsPerDay, xlab = "Total Steps Per Day", ylab= "Frequency", bins = 50)
```

The same array can provide the mean and median steps per day:
```{r}
stepsPerDay.mean   <- mean(stepsPerDay)
stepsPerDay.median <- median(stepsPerDay)
```

This tells us:

- Steps per Day (mean): `r stepsPerDay.mean`.
.
## What is the average daily activity pattern?

From the activity data, we create an array of the mean number of steps taken in each timer interval. 
We then plot thiss:
```{r}
avgStepsPerInterval <- tapply(activity$steps, activity$interval, mean, na.rm = TRUE)
intervals           <- levels(as.factor(activity$interval))
plot(intervals, avgStepsPerInterval, type = "l", 
     main = "Average Steps per Time Interval", 
     xlab = "Interval", 
     ylab = "Mean Steps")
```

Using the same array we can find the time interval in which the most steps are recorded:
```{r}
interval.max <- names(which.max(avgStepsPerInterval))
```
The maximum number of steps is taken in interval `r interval.max`.

## Imputing missing values



## Are there differences in activity patterns between weekdays and weekends?
