---
title: "Reproducible Research: Peer Assessment 1"
output: 
  html_document:
    keep_md: true
---


## Loading and preprocessing the data
We use the ```ggplot2``` package to plot the data:
```{r}
library(ggplot2)
```

The data is a available in a ZIP file, we can extract the data and read it in to a data frame:
```{r}
unzip("activity.zip")
activity <- read.csv("activity.csv")
```

TODO: preprocess

## What is mean total number of steps taken per day?

From the activity data, we create an array of the number of steps taken per day:
```{r }
stepsPerDay <- tapply(activity$steps, activity$date, sum, na.rm = TRUE)
```

We display this this data in a histogram showing the distribution of steps per day.
```{r }
qplot(stepsPerDay, xlab = "Total Steps Per Day", ylab= "Frequency", bins = 30)
```

The same array can provide the mean and median steps per day:
```{r}
stepsPerDay.mean   <- mean(stepsPerDay)
stepsPerDay.median <- median(stepsPerDay)
```

This tells us:

- Steps per Day (mean): `r stepsPerDay.mean`
- Steps per Day (median): `r stepsPerDay.median`

## What is the average daily activity pattern?


## Imputing missing values



## Are there differences in activity patterns between weekdays and weekends?
